---
title: "Basic Template"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, comment = NA)
```

```{r libraries, echo = FALSE, eval = TRUE, warning = FALSE, message = FALSE}
library(ggplot2)
library(ISLR)
library(plotly)
library(tidyr)
library(jtools)
library(olsrr)
library(ggfortify)
library(GGally)
library(tidyverse)
library(ggplot2)
library(dplyr)
library(moderndive)
library(gapminder)
library(skimr)
library(kableExtra)
library(gridExtra)
```

```{r, eval = TRUE}
setwd("/Users/kurisuuu/Downloads")
focus=read.csv("focus.csv")
set.seed(1)
inds <- sample(1:nrow(focus),500) #indices

ford.focus <- focus[inds,] %>% 
  as_tibble() %>% 
  select(-model) %>% 
  mutate_if(is.character,as.factor) %>% 
  mutate(fuelType=as_factor(fuelType),engineSize=as.numeric(engineSize)) %>% 
  select(price,everything())
         
options(knitr.duplicate.label = "allow")
```


# Introduction {#sec:intro}

# Exploratory Data Analysis {#sec:EDA}
```{r, eval = TRUE}
ford.focus %>%
  summarise(n=n(),Mean=round(mean(price),digits=1), St.Dev=round(sd(price),digits=1),
    Min=min(price), Q1 = quantile(price,0.25), Median=median(price),
    Q3 = quantile(price,0.75), Max=max(price)) %>%
kable(caption = '\\label{tab:price} Summary statistics on
  price of 500 UK Used Car Data set.') %>%
kable_styling(latex_options = "hold_position")
```

Table \ref{tab:price} shows that the summaries of price of 500 UK Used Car Data set. For example the mean price 13480.5 pounds. We also note that the variability in the price as 4784.7 pounds. The messages can be easily seen the in the following boxplot which summarise the distribution of car price.

```{r boxplot, out.width = '68%', fig.align = "center",fig.cap = "\\label{fig:box} Price of 500 used Ford cars.", fig.pos = 'H'}
ggplot(ford.focus, aes(y = price)) +
  geom_boxplot() +
  labs(x = "Ford", y = "Price",
    title = "price of 500 UK Used Car Data set")
```


```{r, eval = TRUE}
ford.focus %>%
  summarise(n=n(),Mean=round(mean(mileage),digits=1), St.Dev=round(sd(mileage),digits=1),
    Min=min(mileage), Q1 = quantile(mileage,0.25), Median=median(mileage),
    Q3 = quantile(mileage,0.75), Max=max(mileage)) %>%
kable(caption = '\\label{tab:milage} Summary statistics on
  mileage of 500 UK Used Car Data set.') %>%
kable_styling(latex_options = "hold_position")

```

```{r, eval = TRUE}
ford.focus %>%
  summarise(n=n(),Mean=round(mean(engineSize),digits=1), St.Dev=round(sd(engineSize),digits=1),
    Min=min(engineSize), Q1 = quantile(engineSize,0.25), Median=median(engineSize),
    Q3 = quantile(engineSize,0.75), Max=max(engineSize)) %>%
kable(caption = '\\label{tab:engineSize} Summary statistics on
  engineSize of 500 UK Used Car Data set.') %>%
kable_styling(latex_options = "hold_position")
```


# Formal Data Analysis {#sec:FDA}



# Conclusions {#sec:Conc}

